\cvsection{Experience}
\begin{cventries}
  \cventry
    {Software Developer Engineer Intern @ Aws Open Source}
    {Amazon Web Services}
    {Seattle, Washington}
    {May. 2018 - JULY. 2018}
    {
      \begin{cvitems}
        \item {Development a full stack web dashboard for \textbf{\href{https://github.com/Ab-hay/typeScriptExtension}{Repolinter}}. The project lints open source repositories for common
        issues and provides provider's organization management capabilities.}
        \item {Tooling: Aws Lambda, Aws apigateway, Aws cloudformation, Aws cloudfront, Aws cloudwatch, Reactjs, Nodejs, octokit, Amazon s3}
        \item {Project Status: The service is in Amazons internal production environment and is being use to maintain and monitor health of amazons public repositories. The project is transferred to \textbf{{\href{https://github.com/todogroup/repolinter-dashboard}{todogroup:link}}
        }  }
      \end{cvitems}
    }
  \cventry
    {Coding patterns \& behaviour study}
    {Undergraduate Research, Prof. Timothy Richards}
    {Amherst, Massachusetts}
    {Jan. 2017 - May. 2018}
    {
      \begin{cvitems}
        \item {Developed a visual studio code extension using typescript/nodejs and vscode libraries to collect real time data for understanding coding patterns among Umass Cs students.}
        \item {\textbf{\href{https://github.com/Ab-hay/typeScriptExtension}{Github:link}}}
      \end{cvitems}
    }
  \cventry
    {CS 365: Digital Forensics \textbf{\href{https://people.cs.umass.edu/~liberato/courses/2018-spring-compsci365+590f/syllabus#what-when-where-who}{ Course Website}
    }}
    {Undergraduate Course Assistant, Prof. Marc Liberatore}
    {Amherst, Massachusetts}
    {Jan. 2017 - May. 2018}
    {
      \begin{cvitems}
        \item{Spent 4-5 hours per week mentoring 80+ Cs students. Led labs and small group discussion.}
        \item {Responded to student questions (in-person, email, boards, online platforms).}
        \item{
        Graded class assignments and proctored exams. 
        }
      \end{cvitems} 
    }
  \cventry
    {Software Developer Engineer Intern @ Aws Open Source}
    {Amazon Web Services}
    {Seattle, Washington}
    {May 2017 - AUG. 2017}
    {
      \begin{cvitems}
        \item {Worked on a tool that tracks external contributions to third-party open source software and CLAs that are sometimes associated.}
        \item {Tooling: Nodejs, React, Postgres, typescript, docker, Ldap}
        \item {Project Status: Open sourced on github under Amazon( \textbf{\href{https://github.com/amzn/oss-contribution-tracker}{Github:link}}). The project is also getting used by many other companies like huawei}
      \end{cvitems}
    }
  \cventry
    {Software Developer Engineer Intern @ BasePricing}
    {Amazon (Retail Systems)}
    {Seattle, Washington}
    {JUNE. 2016 - AUG. 2016}
    {
      \begin{cvitems}
        \item { Developed a full stack web service from scratch for Amazon Retail Systems and Services which enables team members to Create, Update and View Amazon.com product configurations. These configuration/objects are used by the Pricing Engine to generate price.}
        \item {Tooling:Java, Spring MVC, Thymeleaf, D3js, Jquery, Json Editor, Google guava, Jackson/Gson, Amazon s3}
        \item {Project Status: The service is in internal production environment and is currently being used by Amazon Software Development Engineers and has improved their work efficiency}
      \end{cvitems}
    }
  
\end{cventries}
